Improving the Image Acquisition Rate of an Atomic Force Microscope Through Compressive Sampling

### 2019-05-29 latex/afm-cs-main.tex
Minor edits

\todo{seems like a waste of space to reprint the algo, since its really no different than the reference}
\begin{algorithm}
  \SetKwInOut{Initialize}{Initialize} \SetKwInOut{Output}{Output}

  \Initialize{$x \in Q_p, \mu=0.9||W x_0||_{\infty}$, $L_{\mu} = \frac{1}{\mu}||W||^2_2$}
    % $x^{k+1} = x^{k}$\\
  \While{$\mu < \mu_{\textrm{final}}$ } {
    $k=0$\\
      \While{$\Delta f_{\mu} > \delta$} {
        $\alpha_k = \frac{1}{2}(k+1)$ \\
        $\tau_k = \frac{2}{k+3}$ \\
        $\displaystyle y_k = \text{arg } \min_{x\in Q_p}
          \frac{L_{\mu}}{2}||x - x_k||_2^2 + \langle \nabla f(x_k),~ x\rangle$\\
        $\displaystyle {z_k = \text{arg } \min_{x\in Q_p} \frac{L_{\mu}}{2}||x-x_0||_2^2 +
        \langle \sum_{i=0}^k \alpha_i \nabla f(x_i), ~x \rangle}$\\
        $x_{k+1} = \tau_kz_k + (1-\tau_k)y_k$\\
        $k \leftarrow k + 1$\\
      }
      $x_0 = x_k$\\
      $\mu = \gamma \mu$\\
      $L_{\mu} = (1/\mu)||W||^2_2$
    }
  \Output{Reconstruction $x_k$}
  \caption{NESTA algorithm}
  \label{ag:NESTA}
\end{algorithm}

@@

% =========================================================================
\section{Control}\label{sec:control}
The control structure for each axis is different. For the $X$-axis, we use a
state space controller. It is described fully in \cite{braker_afmmpc_2019} and
achieves a bandwidth of about 150 Hz, which is over 1/3 of the first $X$-axis
resonance at 350 Hz.

@@

\subsection{Cantilever does not need to fully disengage.}
\todo{Dramatically truncate this section}
In our initial implementation \cite{braker_hardware_2018}, we insisted that the during tip-retraction
(state-5), the cantilever tip should fully break contact with the surface. Here,
we impose no such requirement. Rather, we change the $Z$-setpoint during
tip-retraction to only pull away far enough that the deflection signal stays low
(i.e., below the scanning setpoint), even while we run across the surface. We choose \rzup so that the interaction between the tip and sample becomes purely adhesive. In general, stable imaging in is not possible at \rzup and complete dis-engagement occasionally occurs.

\todo{Not clear to me that friction is useful if I scan parallel to cantilever. Also not clear to me that the normal force and shear force are orthogonal concepts. Maybe the macroscopic analogy breaks down, but thinking of a knife pushed into a surface and then dragged...}

@@

The goal of the SSIM is to compare two image's structure, luminescence, and contrast and is built up from the means ($\mu_x$ and $\mu_y$), standard deviations ($\sigma_x$ and $\sigma_y$), and covariance ($\sigma_{xy}$) of the image vectors $x$ and $y$.  
The variation of the SSIM used in this paper is defined as
\begin{equation*}
  \text{SSIM}(x,y) = \frac{(2\mu_x\mu_y + C_1)(2\sigma_{xy}+C_2)}
  {(\mu_x^2 + \mu_y^2 + C_1)(\sigma_x^2 + \sigma_y^2 + C_2)}
\end{equation*}
where the constants $C_1$ and $C_2$ are regularizing constants to prevent singularity if, e.g., $\mu_x=\mu_y=0$. We use the default values suggested in \cite{wang_image_2004} of $C_1=(0.01L)^2$ and ${C_2=(0.03L)^2}$, where again, $L$ is the dynamic range.

In general two images which are identical will yield an infinite PSNR and an SSIM of 1.

\subsection{Limitations of SSIM and PSNR}\label{sec:limits}
\todo{Should probably remove this entire section?}

What kind of numbers are reasonable to expect from the SSIM and PSNR metrics?
To answer this question, we compare a sequence of 1~Hz raster scans.
In this experiment, (Fig. \ref{fig:rast_unaligned_1}) we took 6 raster scans of the same 5 by 5 micron
square of the CS-20NG sample grating. These scans were taken sequentially and
the NPXY100A remained in closed-loop throughout the process.
Fig.~\ref{fig:rast_unaligned_1} shows the error between the master
image and the remaining 6 images.
Temporally, the images are order left-to-right and top-to-bottom.
Thus we can see, both visually and via the metrics, that in Fig.~\ref{fig:rast_unaligned_1} the mis-alignment
grows over time.

>>>>

\begin{algorithm}
  \SetKwInOut{Initialize}{Initialize} \SetKwInOut{Output}{Output}

  \Initialize{$x \in Q_p, \mu=0.9||W x_0||_{\infty}$, $L_{\mu} = \frac{1}{\mu}||W||^2_2$}
    % $x^{k+1} = x^{k}$\\
  \While{$\mu < \mu_{\textrm{final}}$ } {
    $k=0$\\
      \While{$\Delta f_{\mu} > \delta$} {
        $\alpha_k = \frac{1}{2}(k+1)$ \\
        $\tau_k = \frac{2}{k+3}$ \\
        $\displaystyle y_k = \text{arg } \min_{x\in Q_p}
          \frac{L_{\mu}}{2}||x - x_k||_2^2 + \langle \nabla f(x_k),~ x\rangle$\\
        $\displaystyle {z_k = \text{arg } \min_{x\in Q_p} \frac{L_{\mu}}{2}||x-x_0||_2^2 +
        \langle \sum_{i=0}^k \alpha_i \nabla f(x_i), ~x \rangle}$\\
        $x_{k+1} = \tau_kz_k + (1-\tau_k)y_k$\\
        $k \leftarrow k + 1$\\
      }
      $x_0 = x_k$\\
      $\mu = \gamma \mu$\\
      $L_{\mu} = (1/\mu)||W||^2_2$
    }
  \Output{Reconstruction $x_k$}
  \caption{NESTA algorithm}
  \label{ag:NESTA}
\end{algorithm}
  \todo{seems like a waste of space to reprint the algo, since its really no different than the reference}

@@

% =========================================================================
\section{Control}\label{sec:control}
The control structure for each axis is different. For the $X$-axis, we use a
state space controller. It is described fully in \cite{braker_afmmpc_2019} and
achieves a bandwidth of about 150 Hz, which is over 1/3 of the first $X$-axis
resonance at 350 Hz.
\todo{Not sure how to give a deeper summary without getting to much into the weeds.}

@@

\subsection{Cantilever does not need to fully disengage.}
\todo{Not clear to me yet that friction is useful if I scan parallel to cantilever.
  Also not clear to me that the normal force and shear force are orthogonal concepts.
  Maybe the macroscopic analogy breaks down, but thinking of a knife pushed into a surface and then dragged...}
In our initial implementation \cite{braker_hardware_2018}, we insisted that the during tip-retraction
(state-5), the cantilever tip should fully break contact with the surface. Here,
we impose no such requirement. Rather, we change the $Z$-setpoint during
tip-retraction to only pull away far enough that the deflection signal stays low
(i.e., below the scanning setpoint), even while we run across the surface.
We choose \rzup so that the interaction between the tip and sample becomes purely adhesive.
In general, stable imaging in is not possible at \rzup and complete dis-engagement occasionally occurs.

@@

The goal of the SSIM is to compare two image's structure, luminescence, and contrast and is built up from the means ($\mu_x$ and $\mu_y$), standard deviations ($\sigma_x$ and $\sigma_y$), and covariance ($\sigma_{xy}$) of the image vectors $x$ and $y$.  
The variation of the SSIM used in this paper is defined as
\begin{equation*}
  \text{SSIM}(x,y) = \frac{(2\mu_x\mu_y + C_1)(2\sigma_{xy}+C_2)}
  {(\mu_x^2 + \mu_y^2 + C_1)(\sigma_x^2 + \sigma_y^2 + C_2)}
\end{equation*}
where the constants $C_1$ and $C_2$ are regularizing constants to prevent singularity if, e.g., $\mu_x=\mu_y=0$.
We use the default values suggested in \cite{wang_image_2004} of $C_1=(0.01L)^2$ and ${C_2=(0.03L)^2}$, where again, $L$ is the dynamic range.
In general two images which are identical will yield an infinite PSNR and an SSIM of 1.

\subsection{Limitations of SSIM and PSNR}\label{sec:limits}
What kind of numbers are reasonable to expect from the SSIM and PSNR metrics?
To answer this question, we compare a sequence of 1~Hz raster scans.
In this experiment, (Fig. \ref{fig:rast_unaligned_1}) we took 6 raster scans of the same 5 by 5 micron
square of the CS-20NG sample grating. These scans were taken sequentially and
the NPXY100A remained in closed-loop throughout the process.
Fig.~\ref{fig:rast_unaligned_1} shows the error between the master
image and the remaining 6 images.
Temporally, the images are order left-to-right and top-to-bottom.
Thus we can see, both visually and via the metrics, that in Fig.~\ref{fig:rast_unaligned_1} the mis-alignment
grows over time. 
\todo{Should probably remove this entire section?}
